\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\begin{document}
\pagestyle{empty}

\begin{center}
\Large{\textbf{Appendix E: Calibration and Validation Protocol for the SDT Cosmological Model}}
\end{center}

\vspace{1em}

\textbf{Objective:}
To provide a complete, data-driven protocol for calibrating and validating the Spatial Displacement Theory (SDT) model of cosmological redshift.  
The procedure reconstructs the spation-strain rate $\sigma(z)$ and angle-coupling $\beta(z)$ functions from observational data and tests their consistency against the three canonical probes of cosmology: Supernovae Type Ia (SNe Ia), Baryon Acoustic Oscillations (BAO), and the Cosmic Microwave Background (CMB).

\vspace{1em}

\section*{1. Theoretical Framework}

Redshift and angular magnification are expressed as path integrals over affine distance $L$:
\begin{equation}
\ln(1+z)=\int_{0}^{L}\sigma(r)\,dr,
\qquad
\ln(A)=\int_{0}^{L}\beta(r)\sigma(r)\,dr.
\end{equation}
For the galaxy regime ($z\lesssim4$) where $\beta=1$, the derived measures are
\begin{equation}
L(z)=\int_{0}^{z}\frac{dz'}{(1+z')\sigma(z')},
\qquad
D_A(z)=(1+z)L(z),
\qquad
D_L(z)=(1+z)^3L(z).
\end{equation}
At the Clearing (CMB), $\beta\!\to\!\beta_\infty\!\ll\!1$ preserves the acoustic-peak contrast.

\vspace{1em}

\section*{2. Calibration Procedure}

\subsection*{Step 1: Anchor the Local Strain Rate ($\sigma_0$)}
\textbf{Data:} Low-redshift SNe Ia ($z<0.1$).  
\textbf{Procedure:} Fit a straight line to $z(L)$ to obtain the baseline void strain $\sigma_0=H_0/c$.  
\textbf{Typical Value:} $\sigma_0\approx2.33\times10^{-4}\,\mathrm{Mpc^{-1}}$.

\subsection*{Step 2: Reconstruct $\sigma(z)$ from BAO Data}
\textbf{Principle:} The radial BAO spacing constrains the dimensionless interval
\[
\Delta\ln(1+z)_{\rm BAO}(z)\propto\sigma(z).
\]
\textbf{Procedure:} Derive relative strain points from the observed $\Delta z$ values, then fit a smooth, positive function (e.g. cubic-spline or Gaussian-process fit) for $\sigma(z)/\sigma_0$.

\subsection*{Step 3: Cross-Validate with SNe Ia and Angular BAO Data}
\textbf{Data:} Pantheon+ SNe Ia and transverse BAO.  
\textbf{Procedure:}
\begin{enumerate}
\item Integrate Eq.\,(2) to predict $D_L(z)$ and compare with SNe Ia magnitudes.
\item Compute $D_A(z)$ assuming $A(z)=1+z$ and compare with transverse BAO scales.
\end{enumerate}
\textbf{Criterion:} A single, smooth $\sigma(z)$ must yield $\chi^2/\mathrm{dof}\!\approx\!1$ for both datasets.

\subsection*{Step 4: Calibrate the CMB Spike and Decoupling}
\textbf{Data:} Planck 2018 CMB acoustic spectrum.  
\textbf{Procedure:}
\begin{enumerate}
\item Introduce a narrow spike $\sigma_{\rm CLS}$ satisfying  
      $\int_{0}^{L_{\rm CMB}}\sigma(r)\,dr=\ln(1101)\approx7.004$.
\item Use $\beta(r)=1$ for $z\le z_c$ ($z_c\!\approx\!3$) and $\beta(r)\!\to\!\beta_\infty$ for $z>z_c$;  
      adjust $\beta_\infty\!\sim\!10^{-3}$ to match the observed few-percent smoothing of CMB peaks.
\end{enumerate}

\vspace{1em}

\section*{3. Falsification Checklist}

The SDT cosmological model is valid only if all conditions below are met:
\begin{itemize}
\item[\checkmark] A single, smooth, positive $\sigma(z)$ fits radial BAO, transverse BAO, and SNe Ia data simultaneously.  
\item[\checkmark] SNe Ia light-curve dilation follows $s=1+z$.  
\item[\checkmark] Tolman surface-brightness relation obeys $\Sigma\propto(1+z)^{-4}$.  
\item[\checkmark] CMB peak contrast reproduced with small non-zero $\beta_\infty$.  
\item[\checkmark] CMB blackbody spectrum remains achromatic.  
\end{itemize}
Failure of any criterion constitutes falsification in its present form.

\vspace{1em}

\section*{4. Interpretation}

The calibration connects all cosmological observables to a single mechanical variable $\sigma(z)$—the cumulative strain of the spation lattice.  
This replaces the ad-hoc curvature and dark-energy parameters of metric models with a directly measurable physical quantity.  
The success of this fit will decisively determine whether large-scale cosmology is best described as metric expansion or spatial displacement.

\end{document}
